BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-19 tex/5-related-work.tex
Fix technology they use

A common approach in web content extraction is to manually build wrappers for the targeted websites. This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorises web sites according to the technology they use \TODO{something better than "technology they use"...}, and uses this information to obtain an appropriate wrapper from a knowledge base. The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web. Several works try to simplify this process and provide various degree of automation. This is the case of the Stalker algorithm \cite{stalker} which generate wrappers based on user-labelled training examples. Some commercial solution such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a full integrated development environment where the training data set is obtained via a graphical user interface.

>>>>

A common approach in web content extraction is to manually build wrappers for the targeted websites. This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically assigns web sites to predefined categories and gets the appropriate wrapper from a static knowledge base. The limiting factor in this type of approach is the substantial amount of manual work needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of the web. Several works try to simplify this process and provide various degree of automation. This is the case of the Stalker algorithm \cite{stalker} which generate wrappers based on user-labelled training examples. Some commercial solution such as the Lixto project \cite{lixto} simplify the task of building wrappers by offering a full integrated development environment where the training data set is obtained via a graphical user interface.
